---
title: "raber_550_introductory_analysis"
author: "Austin Hammer"
date: "9/12/2019"
output:
  pdf: default
  '".pdf"': default
---

```{r setup, include=TRUE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
library("ggplot2")
library("phangorn")
library("phyloseq")
library("ape")
library("Rcpp")
library("readxl")
library("dplyr")
library("vegan")
library("metacoder")
library("DESeq2")
library("edgeR")
library("BiodiversityR")
library("DECIPHER")
library("MASS")
library(tibble)
library(knitr)

# Setting ggplot2 theme
theme_set(theme_bw())

# I want to read in the file and just figure out what it looks like after
# unpacking it from the RDS file format

seqtab <- readRDS("C:/Users/hammera/Desktop/raber_550/data/reads_290190_seqtab_final.rds")
seqtab.taxa <- readRDS("C:/Users/hammera/Desktop/raber_550/data/reads_290190_taxa_final.rds")
seqtab <- (seqtab)
# check that number of ASVs and taxa rows is the same
ASV_taxa_equal <- ncol(seqtab) == nrow(seqtab.taxa)

print(ASV_taxa_equal)

# read excel metadata in as a data_frame
meta_data <- as.data.frame(read_excel("C:/Users/hammera/Desktop/raber_550/data/550_metadata.xlsx"))
meta_data_revised <- as.data.frame(read_excel("C:/Users/hammera/Desktop/raber_550/data/550_metadata_revised.xlsx"))
meta_data_envfit <- as.data.frame(read_excel("C:/Users/hammera/Desktop/raber_550/data/550_metadata_nosex.xlsx"))
rownames(seqtab) <- meta_data$RaberSID

# set data equal to phyloseq object parameters
# make sure to change the sample data measure based on the metadata used
samples = sample_data(meta_data_revised)
ASV = otu_table(seqtab, taxa_are_rows = FALSE)
TAX = tax_table(seqtab.taxa)

# I had an issue getting the sample names the same and into phyloseq
sample_names(samples) <- sample_names(ASV)

# create a phyloseq object rename ASVs
physeq = phyloseq(ASV, TAX, samples)
dna <- Biostrings::DNAStringSet(taxa_names(physeq))
physeq <- merge_phyloseq(physeq, dna)
taxa_names(physeq) <- paste0("ASV", seq(ntaxa(physeq)))

# sample 93 was wonky in terms of # of reads, and diversity, while 59 had some metadata issues
# I ran alpha diversity measures including both of these samples and without, but there was
# no statistically significant association between radiation and alpha diversity when they were
# included vs when they weren't
physeq = subset_samples(physeq, sample_names(physeq) != "93")
physeq = subset_samples(physeq, sample_names(physeq) != "59")

# makes a histogram of the reads, and tests for normality using Shapiro-Wilks
# result yields a p-value of 0.44 and suggests that the the data is from a normal distribution
hist(sample_sums(physeq))
shapiro.test(sample_sums(physeq))

# set physeq1 equal to physeq
physeq1 <- physeq

# Change the alpha diversity measure, assign it to a matrix, use shapiro.test to test for normality of alphadiv
# only a couple of alpha diversity measures followed a normal distribution
plot_richness(physeq, x="Treatment", color="Treatment")
```{r, echo=TRUE}
plot_richness(physeq, x="Treatment", color="Treatment")
```

sample_data(physeq1)$Alphadiv <- estimate_richness(physeq1, split=TRUE, measures=c("Shannon"))

alphadiv <- as.matrix(sample_data(physeq1)$Alphadiv)

shapiro.test(alphadiv)

# start visualizing  how alphadiv might vary as a function of radiation status
# I categorized each Radation exposure, and used the MWU test to look for connections with alpha diversity
# Simpson, Shannon, ACE, Chao1, InvSimpson, and Fisher were all evaluated
# Perhaps perform alphadiversity analyses on the rarefied data to see if the results recapitulate those from Keaton and the MPTP data
sample_data(physeq1)$Radiated <- get_variable(physeq1, "Treatment") %in% c("25","50","200")
sample_data(physeq1)$Alphadiv <- estimate_richness(physeq1, split=TRUE, measures=c("Shannon"))
radiated <- sample_data(physeq1)$Radiated
alphadiv <- as.matrix(sample_data(physeq1)$Alphadiv)

# using ANOVA to look at how alphadiv varies as a result of treatment (checked for normality above)
# after rarefaction, still didn't find a significant association
# between Alphadiv and Treatment/Radiation
anova_df <- data.frame(sample_data(physeq1))
aov_results <- aov(as.matrix(Alphadiv) ~ Treatment, data=anova_df)
anova_results <- anova(aov_results)
some_plot <- boxplot((as.matrix(Alphadiv))~Treatment, data=anova_df)
print(anova_results)
summary(anova_results)

# Looking at alpha diversity (Shannon) as a function of radiation
# after rarefaction, I still didn't find any significant difference between Radiation exposed and sham radiation
wilcox.test(alphadiv ~ radiated)

# split up Treatment into the 4 factors
sample_data(physeq1)$Treatment <- as.factor(sample_data(physeq1)$Treatment)

```{r, echo=TRUE}
first_box <- boxplot(alphadiv ~ radiated, outline=FALSE, color=sample_data(physeq1)$Treatment)
show_dots<- stripchart(alphadiv ~ radiated, vertical = TRUE, 
    method = "jitter", add = TRUE, pch = 20, col =c("darkslategray", "orangered4"))
```
    


```{r, echo=TRUE}
boxplot(as.matrix(sample_data(physeq1)$Alphadiv) ~ sample_data(physeq1)$Treatment, outline=FALSE)
stripchart(as.matrix(sample_data(physeq1)$Alphadiv) ~ sample_data(physeq1)$Treatment, vertical = TRUE, 
    method = "jitter", add = TRUE, pch = 20, col=c("slateblue3", "tomato3", "darkolivegreen", "coral4"))
```

# try some linear regression to observe association between alphadiv ~ Treatment, no association, pval=0.1168
# I tried to see if there was a linear model that fits the data above, FSTTimeImmobile had a pval of 0.04677, but the model plot is unusual looking
covariates <- c("Sex", "Treatment", "AMDarkAverage", "OFTotDistDay1", "OFCentDur1", "NOObjpref", "FSTTimeImmobile", "FCCuedFrzTone", "Radiated")
lm_of_alphadiv <- lm(alphadiv ~ sample_data(physeq1)$Sex_Treatment)
summary(lm_of_alphadiv)
plot(lm_of_alphadiv)

# ordination by radiation
# coloring based on the "Radiated" sample data didn't reveal much
# F vs F+R also doesn't appear to change much visually, but check that
# with some real numbers/analysis
physeq1.ord <- ordinate(physeq1, "NMDS", "jaccard")
physeq1.ord.plot.treatment <- plot_ordination(physeq1, physeq1.ord, type="samples", color="Sex_Treatment", title="ByTreatment")

```{r physeq_ord_w_ellipse, echo=TRUE}
# This displays a plot of the ordination
plot(physeq1.ord, type="p")
ordiellipse(physeq1.ord, groups=sample_data(physeq1)$Treatment, scaling="symmetric", conf=0.95, col=c("slateblue3", "tomato3", "darkolivegreen", "coral4"), label=TRUE)
```


```{r, echo=TRUE}
print(physeq1.ord.plot.treatment)
```

physeq1.ord.plot <- plot_ordination(physeq1, physeq1.ord, type="samples", color="Sex", title="BySex", shape="Treatment")
print(physeq1.ord.plot)
physeq1_ord_with_ellipses <- plot_ordination(physeq1, physeq1.ord, type="samples", color="Sex_Treatment", shape="Sex")
physeq1_ord_with_ellipses + stat_ellipse(level=0.3)
physeq1.rda <- rda(otu_table(physeq1))
treatment.env <- data.frame(sample_data(physeq))
physeq1.enfit <- envfit(physeq1.rda~Sex+Treatment+FSTTimeImmobile+NOObjpref+OFCentDur1+FCCuedFrzTone+OFTotDistDay1, data=(treatment.env), perm=5000)
plot(physeq1.rda, type="p")
plot(physeq1.enfit)

physeq1.cca <- (cca(otu_table(physeq1)~Treatment+FSTTimeImmobile+NOObjpref+OFCentDur1+FCCuedFrzTone+OFTotDistDay1, data=treatment.env))
plot(physeq1.cca)


```{r, echo=TRUE}
print(physeq1.ord.plot) + stat_ellipse(level=0.6)
```

# using PERMANOVA(adonis) on a distance matrix, perms=5000
#           Df SumsOfSqs MeanSqs F.Model      R2 Pr(>F)   
# Radiated   1    0.4453 0.44529  1.4346 0.01488  0.0016 **
# Treatment  3    1.2333 0.41109  1.3321 0.04120  2e-04 ***
# Sex        1    0.6266 0.62660  2.0312 0.02093  2e-04 ***
# Box        1    0.6767 0.67668  2.1973 0.02261  2e-04 ***
covariates <- c("Sex", "Treatment", "AMDarkAverage", "OFTotDistDay1", "OFCentDur1", "NOObjpref", "FSTTimeImmobile", "FCCuedFrzTone", "Radiated")
set.seed(1)
physeq1 <- rarefy_even_depth(physeq1)
physeq1.dist <- vegdist(otu_table(physeq1), method="bray")
sampledf <- data.frame(sample_data(physeq1))
set.seed(1)
perm.results.treatment <- adonis(physeq1.dist ~ Box, data=sampledf, permutations=5000)
perm.results.treatment

# plotting betadispersion
treatments <- factor(sample_data(physeq1)$Sex_Treatment)
betadispersion <- betadisper(physeq1.dist, treatments, type=c("centroid"))
plot(betadispersion)
beta_disp_tukey_result <- TukeyHSD(betadispersion, ordered=FALSE, conf.level=0.95)
print(beta_disp_tukey_result)
beta_disp_0 <- c(betadispersion$distances[betadispersion$group == "0"])
beta_disp_25 <- c(betadispersion$distances[betadispersion$group == "25"])
beta_disp_50 <- c(betadispersion$distances[betadispersion$group == "50"])
beta_disp_200 <- c(betadispersion$distances[betadispersion$group == "200"])
# pvalue for shapiro-wilks is extremely low, so there is good evidence to reject the null hypothesis that the sampled values are from a normal distribution
# Does this invalidat the Tukey result earlier? I think that requires a normal distribution
shapiro.test(as.numeric(betadispersion$distances))

# The code above gave a result that suggests only the 200-50 group is significantly different, running this on Sex_Treatment yields a significant adjusted p-val for only F50 and M200/F200
# As there is not a significant difference between groups other than F50 and M200/F200, significant differences in beta-diversity are (mostly?) not attributable to differences in dispersion


```{r, echo=TRUE}
plot(betadispersion)
```

#pvalue <0.05 for test below, permutest is basically anova in the vegan package
# 
set.seed(1)
testbetad <- permutest(betadispersion, pairwise=TRUE, permutations=5000)
anova(betadispersion)
indiv_group <- betadispersion$distances
print(indiv_group)
print(betadispersion$distances[group["0"]])

```{r, echo=TRUE}
boxplot(betadispersion, outline=FALSE)
```


```{r, echo=TRUE}
print(physeq1.ord.plot.treatment)
```


# Time to rarefy and take a peek at how things might change
# miniumum reads observed (trimmed read 93) were 16513, so rarefaction occurs at that point
row_sums <- rowSums(otu_table(physeq1))
hist(row_sums)
set.seed(1)
physeq_rare <- rarefy_even_depth(physeq)

# 4053 (loss of 37 ASVs from physeq1)
ntaxa(physeq_rare)

# I went through and looked at how covariates might
# associate with radiation exposure I did find 200cGy grouped a little
# tighter in the nmds plotting post-rarefaction, and showed a statistically
# significant effect based on the PERMANOVA results
sample_data(physeq_rare)$Treatment <- as.factor(sample_data(physeq_rare)$Treatment)
physeq_rare.ord <- ordinate(physeq_rare, "NMDS", "jaccard", weighted=TRUE)
physeq_rare.ord.plot.treatment <- plot_ordination(physeq_rare, physeq_rare.ord, type="samples", color="Sex_Treatment", title="ByTreatment")

print(physeq_rare.ord.plot.treatment) + stat_ellipse(level=0.4)
```{r, echo=TRUE}
print(physeq_rare.ord.plot.treatment) + stat_ellipse(level=0.4)
```


# Here's some numbers on the plot above with physeq_rare.dist ~ Treatment (R2=.0461, Pr(>F)=2e-04, bray)
# p-values for the following covariates using rarefied data are "Sex"=2e-04, "Treatment"=0.0005999, "AMDarkAverage"=(too many zeros, so it was trimmed), "OFTotDistDay1"=0.7485, "OFCentDur1"=0.3543, "NOObjpref"=0.3583, "FSTTimeImmobile"=0.3603, "FCCuedFrzTone"=0.1012, "Radiated")
# Box=2e-04
# For all of these Treatment has easily the largest R2 value, but it is ~0.04
# The most significant drivers of community structure according to the analyses in Adonis are Treatment, Sex, and Box. Running adonis with different permutations of these three covariates shows that Treatment remains the covariate with the largest R2 value
physeq_rare_dist <- vegdist(otu_table(physeq_rare), method="jaccard")
sampledf <- data.frame(sample_data(physeq_rare))
set.seed(1)
perm.results.treatment.rare <- adonis(physeq_rare_dist ~ Box*Sex + Treatment, data=sampledf, permutations=5000)
perm.results.treatment.rare

# under jaccard the results don't change much for Treatment, but it is interesting to note that
# the R2 suggests Treatment accounts for nearly 2x the variation as Box or bodyweight


# Give agglomeration a tick, and see what your results are saying
# At each rank, K=2, P=12, C=18, O=24, F=39, G=91, S=(obvious)
physeq1_glom <- tax_glom(physeq1, taxrank="Genus")
ntaxa(physeq1_glom)
physeq1_glom

sample_data(physeq1_glom)$Treatment <- as.factor(sample_data(physeq1_glom)$Treatment)
physeq1_glom.ord <- ordinate(physeq1_glom, "NMDS", "jaccard", weighted=TRUE)
physeq1_glom.ord.plot.treatment <- plot_ordination(physeq1_glom, physeq1_glom.ord, type="samples", color="Treatment", title="ByTreatment")

```{r, echo=TRUE}
physeq1_glom.ord.plot.treatment + stat_ellipse(alpha=0.6)
```

physeq1glom.dist <- vegdist(otu_table(physeq1_glom), method="jaccard")
sampledfglom <- data.frame(sample_data(physeq1_glom))
physeq1_glom
set.seed(1)
perm.results.phyglom <- adonis(physeq1glom.dist ~ Treatment*Bodyweight, data=sampledfglom, permutations=5000)
perm.results.phyglom

# Making a network, maybe for the academic/exploratory sake of doing it
glom_network <- make_network(physeq1_glom, type="samples")
glom_network_plot <- plot_network(glom_network, physeq1_glom, color="Treatment")

```{r, echo=TRUE}
print(glom_network_plot)
```
# it was a bit interesting to see the network that relates Treatment 200
# the default for distance is jaccard, and the default distance cutoff is 0.4
# play around with this to see what it looks like at a higher cutoff value
# this plot uses the agglomerated data, it's kind of interesting that there looks like there is still structure, 
# although this isn't verified by adonis results for treatment
# Really intersting that using the F reads was able to link many of the disparate samples together, particuarly those that come from the highly divergent 50cgy group

# Trying Deseq2
# I used this as a quick and dirty test at a couple of different agglomeration levels to test for significance
# Running this with some of the covariates yields
# ASV987 (Romboutsia - Genus, Peptostreptococcaceae - Family) (https://www.nature.com/articles/s41598-018-32413-2, recent article on its possible use as a biomarker for intestinal cancers) and ASV 1082 (Ruminococcaceae-UCG-009, reduction in this genus was associated with post-operative delirium in mice, https://onlinelibrary.wiley.com/doi/full/10.1111/cns.13103, it appears to be found broadly in a wide variety of organisms, it's also positively associated with low-grade inflammation related to aging in some animals https://www.frontiersin.org/articles/10.3389/fmicb.2019.01803/full)
# Maybe running this on the F reads would give a slightly more robust representation of how genera are changing? Especially because I've been using Jaccard, agglomerating with more Forward ASVs might be more sensitive to compositional changes
# Need to go through and plot how counts change between treatments to get a better visual idea of what's happening here

# Some covariates to consider are "Sex", "Treatment", "AMDarkAverage", "OFTotDistDay1", "OFCentDur1", "NOObjpref", "FSTTimeImmobile", "FCCuedFrzTone", "Radiated"
sigtab <- NULL
treatdds = phyloseq_to_deseq2(physeq_rare, ~Bodyweight)
treatdds.deseq = DESeq(treatdds)
res = res[order(res$padj, na.last=NA), ]
alpha = 0.01
sigtab = res[(res$padj < alpha), ]
sigtab = cbind(as(sigtab, "data.frame"), as(tax_table(physeq1)[rownames(sigtab), ], "matrix"))
print(sigtab)
sigtabgen = subset(sigtab, !is.na(Genus))
# Phylum order
x = tapply(sigtabgen$log2FoldChange, sigtabgen$Phylum, function(x) max(x))
x = sort(x, TRUE)
sigtabgen$Phylum = factor(as.character(sigtabgen$Phylum), levels=names(x))
# Genus order
x = tapply(sigtabgen$log2FoldChange, sigtabgen$Genus, function(x) max(x))
x = sort(x, TRUE)
sigtabgen$Genus = factor(as.character(sigtabgen$Genus), levels=names(x))
ggplot(sigtabgen, aes(y=Genus, x=log2FoldChange, color=Phylum)) + 
  geom_vline(xintercept = 0.0, color = "gray", size = 0.5) +
  geom_point(size=6) + 
  theme(axis.text.x = element_text(angle = -90, hjust = 0, vjust=0.5))

# Are the significant ASVs that I find from the F reads the same as the merged?
print(taxa.results[taxa.results<0.005 & is.numeric(taxa.results)])
signif_taxa <- (otu_table(physeq1_glom))



# Capscale -> Ordistep for comparison of models (consider using physeq_rare_dist as well)
# log of AIC results for different permutations of covariates 
#Box+Sex+Treatment+FSTTimeImmobile
#                   Df    AIC      F Pr(>F)
#  FSTTimeImmobile  1 334.83 1.0317   0.34
# Box+Sex+Treatment
# Start: physeq_rare_dist ~ Box + Sex + Treatment 

#            Df    AIC      F Pr(>F)   
#- Treatment  1 331.92 1.1568  0.060 . 
#- Sex        1 332.11 1.3398  0.010 **
#- Box        1 332.14 1.3667  0.005 **


##("Sex", "Treatment", "AMDarkAverage", "OFTotDistDay1", "OFCentDur1", "NOObjpref", "FSTTimeImmobile", "FCCuedFrzTone", "Radiated")


# CLUSTERING
# single linkage clustering
abund_table_norm <- decostand(abund_table, "normalize")
jacc_dist <- vegdist(abund_table_norm, method="jaccard")
cluster_single <- hclust(jacc_dist, method='single')
plot(cluster_single)

# complete linkage agglomerative clustering
# "farthest neighbor clustering", allows clustering only at a distance that samples are farthest apart from each other
cluster_complete <- hclust(jacc_dist, method='complete')
plot(cluster_complete)

# Ward's minimum variance clustering
# minimizes sum of squares distances between samples
# basically treats it like an ANOVA problem instead of using distance metrics
cluster_ward <- hclust(jacc_dist, method='ward.D2')
plot(cluster_ward)

# look at the results from the above clustering together
par(mfrow=c(1,3))
plot(cluster_single)
plot(cluster_complete)
plot(cluster_ward)

# Other ordinations
# Super low eigenvalues for PC1,2,3,etc. with low inertia as well. (0.0002/0.0033) ~6% variation in PC1
stand_abund_table <- decostand(abund_table, method="total")
PCA <- rda(stand_abund_table)
PCA
sum(apply(stand_abund_table,2,var))
biplot(PCA, display='sites')
ordiplot(PCA, display="sites", type="text")
head(otu_table(physeq))







## I ran through all of the covariates listed 
sampledf <- data.frame(sample_data(physeq1))
physeq.capsca <- capscale(physeq_rare_dist ~ Treatment*Sex, sampledf, dist="jaccard")
set.seed(1)
mod <- ordistep(physeq.capsca, perm.max = 5000, trace = T, direction = "both")


# see this webpage and try a derivative of the following function
# https://stats.stackexchange.com/questions/323968/theta-going-towards-infinity-in-negative-binomial-model
foo <- function() {
  m0 <- glm.nb(y~group)
  if (m0$th.warn == "iteration limit reached") {
    m0 <- glm(y~group, family=poisson)
  }
  m0
}
physeq1_glom <- tax_glom(physeq1, taxrank="Order")
# Write up some code for taxon analysis
# First step is to normalize the reads, should I set a threshold in a future step to eliminate low-abundance taxa? This is something that is done in the phyloseq tutorial, and generally a pre-processing step that is used, it would probably change beta-div measures significantly
plot_taxa_physeq1 <- taxa_sums(physeq1)
plot(plot_taxa_physeq1)
physeq1_section <- otu_table(physeq1)
# Make sure this setting is correct
physeq1 <- physeq_rare
ncol(otu_table(physeq1))

# Because there are a bunch of  taxa that show up infrequently, I'm going to prune taxa and proceed for the glm_nb stuff
plot_taxa_physeq1 <- taxa_sums(physeq1)
plot(plot_taxa_physeq1)
# Make sure that at each run, you specify how this is change and track the minimum number of reads per sample that you use
physeq2 <- physeq_rare
#physeq2 <- prune_taxa(taxa_sums(physeq2)>1000, physeq2)
plot(taxa_sums(physeq2))
# in the code below, x is a phyloseq_object, y and z are covatiates to analyze in GLM1/2
#glm_nb_for_taxa <- function (x, y, z){
require("MASS")
require("phyloseq")
#colnames(results) <- c("ASV_name", "glm1", "glm2")
#physeq2 <- transform_sample_counts(physeq2, function(y) y / sum(y))
ASVs_to_analyze <- otu_table(physeq2)
ASV_names <- colnames(otu_table(physeq2))
sample_metadata <- sample_data(physeq2)
taxa_info <- tax_table(physeq2)
super_df <- cbind(ASVs_to_analyze, sample_metadata)
otus <- names(super_df[1:length(ASV_names)])
## The code below will only execute for 126 ASVs, at which point it says that "no valid set of coefficients has been found" and asks me to supply starting values. It also notes that there were like 50 warnings.
results = NULL
glm1_vec <- NULL
glm2_vec <- NULL
for (i in 1:ncol(ASVs_to_analyze)) {
#results$ASV_name <- ASV_names[i]
# are the glm results not calculating because the standard error is -infinity? Seems this is a common error online
# basically the analysis tops out at ASV127, not sure what is going on beyond that
#original form glm2 <- glm.nb(super_df[,i]~Treatment*Sex, data=super_df, link=sqrt)
glm1 <- glm.nb((super_df[,i])~Treatment+Sex, data=super_df, link=sqrt)
glm2 <- glm.nb(super_df[,i]~Treatment*Sex, data=super_df, link=sqrt)
glm1_vec = c(glm1)
glm2_vec = c(glm2)
# uses AIC to compare glms for the models listed above
comparison_results <- NULL
comparison_results <- AIC(glm1, glm2)
results <- rbind(results, c(comparison_results$AIC, otus[i]))
}
#return(results)
#}




physeq1_glom <- tax_glom(physeq, taxrank="Genus")
testing_correlate_function = correlate_taxa(physeq1_glom)
## The function below takes a phyloseq object, extracts relevant data, then performs a correlation test using Kendall's tau if you want to use a different method for correlation analysis configure it using method in does_it_correlate
correlate_taxa <- function(phyloseq_object){
require("phyloseq")
#normalize read counts
#phyloseq_object = transform_sample_counts(phyloseq_object, function(y) y / sum(y))
#extract otu table for creation of big df
ASVs_for_analysis <- otu_table(phyloseq_object)
#extract metadata
sample_metadata <- sample_data(phyloseq_object)
#Get a taxa table (if you need it for later analysis)
taxa_info_table <- tax_table(phyloseq_object)
#combine otu_table and treatment info into one df
super_cor_df <- cbind(ASVs_for_analysis, sample_metadata)
#save values in this one
place_to_store_df <- NULL
place_to_store_df$ASV <- colnames(ASVs_for_analysis)
#colnames(place_to_store_df) <- (c("ASV", "saved p-value"))
#loop through the super_df, test each taxa for correlation, save the p-value and ASV in place_to_store_df, and return it after analysis is finished
for (i in 1:ncol(ASVs_for_analysis)){
does_it_correlate <- cor.test(x=(super_cor_df$NOObjpref),y=(super_cor_df[,i]), method=(c("spearman")))
place_to_store_df$pvalue[i] <- does_it_correlate[["p.value"]]
}
return(place_to_store_df)
}


testing_correlate_function = correlate_taxa(physeq_genus)
testing_correlate_function$pvalue = p.adjust(as.numeric(testing_correlate_function$pvalue), method=c("fdr"))
testing_correlate_function = subset(testing_correlate_function, !is.na(testing_correlate_function$pvalue))
print(testing_correlate_function)


##Trying some random forest classification
set.seed(1)
random_forest_df = data.frame("OTU_table" = ASVs_for_analysis, "Treatment" = sample_metadata$Treatment)
modeling <- train(x = ASVs_for_analysis, y =)
