---
title: "raber_550_introductory_analysis"
author: "Austin Hammer"
date: "9/12/2019"
output:
  '".pdf"': default
  pdf: default
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
library("ggplot2")
library("phangorn")
library("phyloseq")
library("ape")
library("Rcpp")
library("readxl")
library("dplyr")
library("vegan")
library("metacoder")
library("DESeq2")
library("edgeR")
library("BiodiversityR")
library("DECIPHER")
library("plyr")
library("MASS")
# Setting ggplot2 theme
theme_set(theme_bw())

# I want to read in the file and just figure out what it looks like after
# unpacking it from the RDS file format

seqtab <- readRDS("C:/Users/hammera/Desktop/raber_550/data/reads_290190_seqtab_final.rds")

seqtab.taxa <- readRDS("C:/Users/hammera/Desktop/raber_550/data/reads_290190_taxa_final.rds")

# check that number of ASVs and taxa rows is the same
ASV_taxa_equal <- ncol(seqtab) == nrow(seqtab.taxa)

print(ASV_taxa_equal)

# read pdf metadata in as a data_frame
meta_data <- as.data.frame(read_excel("C:/Users/hammera/Desktop/raber_550/data/550_metadata.xlsx"))
meta_data_revised <- as.data.frame(read_excel("C:/Users/hammera/Desktop/raber_550/data/550_metadata_revised.xlsx"))
rownames(seqtab) <- meta_data$RaberSID

# set data equal to phyloseq object parameters
# make sure to change the sample data measure based on the metadata used
samples = sample_data(meta_data_revised)
ASV = otu_table(seqtab, taxa_are_rows = FALSE)
TAX = tax_table(seqtab.taxa)

# I had an issue getting the sample names the same and into phyloseq
sample_names(samples) <- sample_names(ASV)

# create a phyloseq object rename ASVs
physeq = phyloseq(ASV, TAX, samples)
dna <- Biostrings::DNAStringSet(taxa_names(physeq))
physeq <- merge_phyloseq(physeq, dna)
taxa_names(physeq) <- paste0("ASV", seq(ntaxa(physeq)))
physeq

# sample 93 was wonky in terms of # of reads, and diversity, while 59 had some metadata issues
# I ran alpha diversity measures including both of these samples and without, but there was
# no statistically significant association between radiation and alpha diversity when they were
# included vs when they weren't
physeq = subset_samples(physeq, sample_names(physeq) != "93")
physeq = subset_samples(physeq, sample_names(physeq) != "59")

# makes a histogram of the reads, and tests for normality using Shapiro-Wilks
# result yields a p-value of 0.44 and suggests that the the data is from a normal distribution
hist(sample_sums(physeq))
shapiro.test(sample_sums(physeq))

# set physeq1 equal to physeq
physeq1 <- physeq

# Change the alpha diversity measure, assign it to a matrix, use shapiro.test to test for normality of alphadiv
# only a couple of alpha diversity measures followed a normal distribution
plot_richness(physeq, x="Treatment", color="Treatment")
```{r, echo=TRUE}
plot_richness(physeq, x="Treatment", color="Treatment")
```

sample_data(physeq1)$Alphadiv <- estimate_richness(physeq1, split=TRUE, measures=c("Shannon"))

alphadiv <- as.matrix(sample_data(physeq1)$Alphadiv)

shapiro.test(alphadiv)

# start visualizing  how alphadiv might vary as a function of radiation status
# I categorized each Radation exposure, and used the MWU test to look for connections with alpha diversity
# Simpson, Shannon, ACE, Chao1, InvSimpson, and Fisher were all evaluated
sample_data(physeq1)$Radiated <- get_variable(physeq1, "Treatment") %in% c("25","50","200")
sample_data(physeq1)$Alphadiv <- estimate_richness(physeq1, split=TRUE, measures=c("Shannon"))
radiated <- sample_data(physeq1)$Radiated
alphadiv <- as.matrix(sample_data(physeq1)$Alphadiv)

# using ANOVA to look at how alphadiv varies as a result of treatment (checked for normality above)
# after rarefaction, still didn't find a significant association
# between Alphadiv and Treatment/Radiation
anova_df <- data.frame(sample_data(physeq1))
anova_results <- aov(as.matrix(Alphadiv) ~ Treatment, data=anova_df)
summary(anova_results)

# Looking at alpha diversity (Shannon) as a function of radiation
# after rarefaction, I still didn't find any significant difference between Radiation exposed and sham radiation
wilcox.test(alphadiv ~ radiated)

# split up Treatment into the 4 factors
sample_data(physeq1)$Treatment <- as.factor(sample_data(physeq1)$Treatment)

```{r, echo=TRUE}
first_box <- boxplot(alphadiv ~ radiated, outline=FALSE, color=sample_data(physeq1)$Treatment)
show_dots<- stripchart(alphadiv ~ radiated, vertical = TRUE, 
    method = "jitter", add = TRUE, pch = 20, col =c("darkslategray", "orangered4"))
```
    


```{r, echo=TRUE}
boxplot(as.matrix(sample_data(physeq1)$Alphadiv) ~ sample_data(physeq1)$Treatment, outline=FALSE)
stripchart(as.matrix(sample_data(physeq1)$Alphadiv) ~ sample_data(physeq1)$Treatment, vertical = TRUE, 
    method = "jitter", add = TRUE, pch = 20, col=c("slateblue3", "tomato3", "darkolivegreen", "coral4"))
```

# try some linear regression to observe association between alphadiv ~ Treatment, no association, pval=0.1168
# I tried to see if there was a linear model that fits the data above, FSTTimeImmobile had a pval of 0.04677, but the model plot is unusual looking
covariates <- c("Sex", "Treatment", "AMDarkAverage", "OFTotDistDay1", "OFCentDur1", "NOObjpref", "FSTTimeImmobile", "FCCuedFrzTone", "Radiated")
lm_of_alphadiv <- lm(alphadiv ~ sample_data(physeq1)$Sex_Treatment)
summary(lm_of_alphadiv)
plot(lm_of_alphadiv)

# ordination by radiation
# coloring based on the "Radiated" sample data didn't reveal much
# F vs F+R also doesn't appear to change much visually, but check that
# with some real numbers/analysis
physeq1.ord <- ordinate(physeq1, "NMDS", "jaccard")
physeq1.ord.plot.treatment <- plot_ordination(physeq1, physeq1.ord, type="samples", color="Treatment", title="ByTreatment")

```{r physeq_ord_w_ellipse, echo=TRUE}
# This displays a plot of the ordination
plot(physeq1.ord, type="p")
ordiellipse(physeq1.ord, groups=sample_data(physeq1)$Treatment, scaling="symmetric", conf=0.95, col=c("slateblue3", "tomato3", "darkolivegreen", "coral4"), label=TRUE)
```


```{r, echo=TRUE}
print(physeq1.ord.plot.treatment)
```

physeq1.ord.plot <- plot_ordination(physeq1, physeq1.ord, type="samples", color="Sex", title="BySex", shape="Treatment")
print(physeq1.ord.plot)
physeq1_ord_with_ellipses <- plot_ordination(physeq1, physeq1.ord, type="samples", color="Sex_Treatment", shape="Sex")
physeq1_ord_with_ellipses + stat_ellipse(level=0.3)
physeq1.dca <- rda(otu_table(physeq1))
treatment.env <- na.omit(sample_data(physeq1))
physeq1.enfit <- envfit(physeq1.dca, env=na.omit(treatment.env), perm=5000)
plot(physeq1.dca, type="n")
plot(physeq1.enfit)
covariates <- c("Sex", "Treatment", "AMDarkAverage", "OFTotDistDay1", "OFCentDur1", "NOObjpref", "FSTTimeImmobile", "FCCuedFrzTone", "Radiated")

```{r, echo=TRUE}
print(physeq1.ord.plot)
```

# using PERMANOVA(adonis) on a distance matrix, perms=5000
#           Df SumsOfSqs MeanSqs F.Model      R2 Pr(>F)   
# Radiated   1    0.4453 0.44529  1.4346 0.01488  0.0016 **
# Treatment  3    1.2333 0.41109  1.3321 0.04120  2e-04 ***
# Sex        1    0.6266 0.62660  2.0312 0.02093  2e-04 ***
# Box        1    0.6767 0.67668  2.1973 0.02261  2e-04 ***
covariates <- c("Sex", "Treatment", "AMDarkAverage", "OFTotDistDay1", "OFCentDur1", "NOObjpref", "FSTTimeImmobile", "FCCuedFrzTone", "Radiated")
physeq1.dist <- vegdist(otu_table(physeq1), method="jaccard")
sampledf <- data.frame(sample_data(physeq1))
# Running the below code with Sex_Treatment yielded an R2 of nearly 10%
set.seed(1)
perm.results.treatment <- adonis(physeq1.dist ~ Sex_Treatment, data=sampledf, permutations=5000)
perm.results.treatment

# plotting betadispersion
treatments <- factor(sample_data(physeq1)$Sex_Treatment)
betadispersion <- betadisper(physeq1.dist, treatments, type=c("centroid"))
plot(betadispersion)
```{r, echo=TRUE}
plot(betadispersion)
```

#pvalue <0.05 for test below, permutest is basically anova in the vegan package
# 
set.seed(1)
testbetad <- permutest(betadispersion, permutations=5000)
testbetad
```{r, echo=TRUE}
boxplot(betadispersion, outline=FALSE)
```

# trying to get envfit function to work
# in order to get this to show up, I would need to trim Mouse 59 and get rid of some columns with data
# check if any of these columns are covariates, maybe visit with Tom about this
physeq1.mds <- isoMDS(physeq1.dist)
physeq1.mds <- postMDS(physeq1.mds, physeq1.dist)
physeq1.fit <- envfit(physeq1.mds, sampledf, na.rm=TRUE)
plot(physeq1.mds$Treatment, pch="+", asp=1, xlab="Dim1", ylab="Dim2")
plot(physeq1.fit)

physeq1.envfit <- envfit(physeq1.dist, sampledf, perm=5000)

```{r, echo=TRUE}
print(physeq1.ord.plot.treatment)
```


# Time to rarefy and take a peek at how things might change
# miniumum reads observed (trimmed read 93) were 16513, so rarefaction occurs at that point
row_sums <- rowSums(otu_table(physeq1))
hist(row_sums)
set.seed(1)
physeq_rare <- rarefy_even_depth(physeq)

# 4053 (loss of 37 ASVs from physeq1)
ntaxa(physeq_rare)

# I went through and looked at how covariates might
# associate with radiation exposure I did find 200cGy grouped a little
# tighter in the nmds plotting post-rarefaction, and showed a statistically
# significant effect based on the PERMANOVA results
sample_data(physeq_rare)$Treatment <- as.factor(sample_data(physeq_rare)$Treatment)
physeq_rare.ord <- ordinate(physeq_rare, "NMDS", "jaccard", weighted=TRUE)
physeq_rare.ord.plot.treatment <- plot_ordination(physeq_rare, physeq_rare.ord, type="samples", color="Treatment", title="ByTreatment")

```{r, echo=TRUE}
print(physeq_rare.ord.plot.treatment)
```


# Here's some numbers on the plot above with physeq_rare.dist ~ Treatment (R2=.0461, Pr(>F)=2e-04, bray)
physeq_rare.dist <- vegdist(otu_table(physeq_rare), method="jaccard")
sampledf <- data.frame(sample_data(physeq_rare))
set.seed(1)
perm.results.treatment.rare <- adonis(physeq_rare.dist ~ Treatment, data=sampledf, permutations=5000)
perm.results.treatment.rare

# under jaccard the results don't change much for Treatment, but it is interesting to note that
# the R2 suggests Treatment accounts for nearly 2x the variation as Box or bodyweight


# Give agglomeration a tick, and see what your results are saying
# At each rank, K=2, P=12, C=18, O=24, F=39, G=91, S=(obvious)
physeq1_glom <- tax_glom(physeq1, taxrank="Genus")
ntaxa(physeq1_glom)
physeq1_glom

sample_data(physeq1_glom)$Treatment <- as.factor(sample_data(physeq1_glom)$Treatment)
physeq1_glom.ord <- ordinate(physeq1_glom, "NMDS", "jaccard", weighted=TRUE)
physeq1_glom.ord.plot.treatment <- plot_ordination(physeq1_glom, physeq1_glom.ord, type="samples", color="Treatment", title="ByTreatment")

```{r, echo=TRUE}
print(physeq1_glom.ord.plot.treatment)
```

physeq1glom.dist <- vegdist(otu_table(physeq1_glom), method="jaccard")
sampledfglom <- data.frame(sample_data(physeq1_glom))
physeq1_glom
set.seed(1)
perm.results.phyglom <- adonis(physeq1glom.dist ~ Treatment*Bodyweight, data=sampledfglom, permutations=5000)
perm.results.phyglom

# Making a network, maybe for the academic/exploratory sake of doing it
glom_network <- make_network(physeq1_glom, type="samples")
glom_network_plot <- plot_network(glom_network, physeq1_glom, color="Treatment")

```{r, echo=TRUE}
print(glom_network_plot)
```
# it was a bit interesting to see the network that relates Treatment 200
# the default for distance is jaccard, and the default distance cutoff is 0.4
# play around with this to see what it looks like at a higher cutoff value
# this plot uses the agglomerated data, it's kind of interesting that there looks like there is still structure, 
# although this isn't verified by adonis results for treatment


# Trying Deseq2
# I used this as a quick and dirty test at a couple of different agglomeration levels to test for significance
# Running this with some of the covariates yields
# ASV987 (Romboutsia - Genus, Peptostreptococcaceae - Family) (https://www.nature.com/articles/s41598-018-32413-2, recent article on its possible use as a biomarker for intestinal cancers) and ASV 1082 (Ruminococcaceae-UCG-009, reduction in this genus was associated with post-operative delirium in mice, https://onlinelibrary.wiley.com/doi/full/10.1111/cns.13103, it appears to be found broadly in a wide variety of organisms, it's also positively associated with low-grade inflammation related to aging in some animals https://www.frontiersin.org/articles/10.3389/fmicb.2019.01803/full)
# Maybe running this on the F reads would give a slightly more robust representation of how genera are changing? Especially because I've been using Jaccard, agglomerating with more Forward ASVs might be more sensitive to compositional changes
# Need to go through and plot how counts change between treatments to get a better visual idea of what's happening here
 
covariates <- c("Sex", "Treatment", "AMDarkAverage", "OFTotDistDay1", "OFCentDur1", "NOObjpref", "FSTTimeImmobile", "FCCuedFrzTone", "Radiated")
treatdds = phyloseq_to_deseq2(physeq1, ~Sex_Treatment)
treatdds.deseq = DESeq(treatdds)
res <- results(treatdds.deseq)
taxa.results <-c(res@listData[["padj"]])

print(taxa.results[taxa.results<0.005 & taxa.results>0])
signif_taxa <- (otu_table(physeq1_glom))
TAX[1082]

# Capscale -> Ordistep for comparison of models (consider using physeq_rare.dist as well)
sampledf <- data.frame(sample_data(physeq1))
physeq.capsca <- capscale(physeq1.dist ~ Box + Sex + Treatment, sampledf, dist="jaccard")
set.seed(1)
ordistep(physeq.capsca, perm.max = 5000)

## IGNORE THE BUSINESS GOING ON HERE, BUILDING A DF FOR ALPHADIV/BETADIV FOR FUTURE ANALYSIS
abund_table <- otu_table(physeq1)
N <- specnumber(abund_table)
df_N <- data.frame(sample=names(N), value=N, measure=rep("Number", length(N)))
CH=estimateR(abund_table)[2,]
df_CH <- data.frame(sample=names(CH), value=CH, measure=rep("Chao1", length(CH)))
H<-diversity(abund_table, "shannon")
df_H<-data.frame(sample=names(H), value=H,measure=rep("Shannon",length(H)))
simp_genus<-diversity(abund_table, "simpson")
df_simp<-data.frame(sample=names(simp_genus),value=simp_genus, measure=rep("Simpson", length(simp_genus)))
S<-specnumber(abund_table)
J<-H/log(S)
df_J<-data.frame(sample=names(J),value=J,measure=rep("Pielou", length(J)))
df_adiv <- rbind(df_N, df_CH, df_H, df_J)

ggplot(df_adiv)

# CLUSTERING
# single linkage clustering
abund_table_norm <- decostand(abund_table, "normalize")
jacc_dist <- vegdist(abund_table_norm, method="jaccard")
cluster_single <- hclust(jacc_dist, method='single')
plot(cluster_single)

# complete linkage agglomerative clustering
# "farthest neighbor clustering", allows clustering only at a distance that samples are farthest apart from each other
cluster_complete <- hclust(jacc_dist, method='complete')
plot(cluster_complete)

# Ward's minimum variance clustering
# minimizes sum of squares distances between samples
# basically treats it like an ANOVA problem instead of using distance metrics
cluster_ward <- hclust(jacc_dist, method='ward.D2')
plot(cluster_ward)

# look at the results from the above clustering together
par(mfrow=c(1,3))
plot(cluster_single)
plot(cluster_complete)
plot(cluster_ward)

# Other ordinations
# Super low eigenvalues for PC1,2,3,etc. with low inertia as well. (0.0002/0.0033) ~6% variation in PC1
stand_abund_table <- decostand(abund_table, method="total")
PCA <- rda(stand_abund_table)
PCA
sum(apply(stand_abund_table,2,var))
biplot(PCA, display='sites')
ordiplot(PCA, display="sites", type="text")
head(otu_table(physeq))

#cor.test with a method of spearman
